### 2020-12-30 docs/submission/srep/coverletter/letter-tex/covlet.tex
polishes README.md; polishes coverletter; updates abstracts and re-submit to arxiv with v04

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled 
"Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities"
authored by Miguel Xochicale and Chris Baber to be considered for publication as a research article 
in your prestigious journal Scientific Reports.

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate to be considered to be published in Scientific Reports due to
its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility).
Similarly, we chosen Scientific Reports because of the outcomes of our work might lead to 
potential applications in areas of natural and clinical science.
Our manuscript is containing original research and has not been submitted or published earlier 
in any journal and is not being considered for publication elsewhere. 
Authors have seen and approved the manuscript and have contributed significantly to it.

>>>>

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled "Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities" authored by Miguel Xochicale and Chris Baber to be considered for publication as a research article in your prestigious journal.

%* A brief explanation of why the work is appropriate for Scientific Reports
Our work is appropriate for Scientific Reports due to its alignment to the principles of open science (e.g., reproducibility, transparency, reusability and open accessibility).   
Similarly, we choose Scientific Reports because of the potential reachability to readers in areas of natural and clinical sciences along with potential application of our work and the spark for collaborations.

Our manuscript is containing original research and has not been submitted or published earlier in any journal and is not being considered for publication elsewhere.   
Authors have seen and approved the manuscript and have contributed significantly to it.
